Title: Reproducible Research: Peer Assessment 1
================================================
### The purpose of this research is to analyse the steps taken by an individual, observed at 5-min intervals that are spread across 2 months.

## Loading and preprocessing the data
```{r}
AMdata <- read.csv("activity.csv")
head(AMdata)
```


## What is total number of steps taken per day?
```{r}
Tdaysteps <- tapply(AMdata$steps, AMdata$date, sum)
hist(Tdaysteps, main = "Total steps taken each day", col="green", xlab="steps taken")
```


## What is the mean number of steps taken per day?
```{r}
Mean.Step <- tapply(AMdata$steps, AMdata$date, mean)
Mean.Step <- as.data.frame(Mean.Step)
Mean.Step
```


## What is the median number of steps taken per day?
```{r}
Median.Step <- tapply(AMdata$steps, AMdata$date, median)
Median.Step <- as.data.frame(Median.Step)
Median.Step
```


## What is the average daily activity pattern?
```{r}
Mean.Step.5MinInt <- aggregate(steps ~ interval, data = AMdata, mean)
plot(Mean.Step.5MinInt, type = "l", col = "green")
```


## Which 5-minute interval contains the maximum number of steps?
```{r}
library(dplyr)
filter(Mean.Step.5MinInt, steps == max(steps))
```


## What is the total number of missing values in the dataset?
```{r}
summary(AMdata)
```
There are 2304 NA values and they are all in the "steps" variable.


## Create a new dataset that is equal to the original dataset but with the missing data filled in
```{r}
NAsteps <- is.na(AMdata$steps)
AMdata$steps[NAsteps] <- 37.38
summary(AMdata)
```


## What is total number of steps taken per day?
```{r}
Tdaysteps <- tapply(AMdata$steps, AMdata$date, sum)
hist(Tdaysteps, main = "Total steps taken each day", col="blue", xlab="steps taken")
```


## What is the mean number of steps taken per day?
```{r}
Mean.Step <- tapply(AMdata$steps, AMdata$date, mean)
Mean.Step <- as.data.frame(Mean.Step)
Mean.Step
```


## What is the median number of steps taken per day?
```{r}
Median.Step <- tapply(AMdata$steps, AMdata$date, median)
Median.Step <- as.data.frame(Median.Step)
Median.Step
```


## What is the impact of imputing missing data on the estimates of the total daily number of steps?
### The mean and median values remain unchanged after the NA values are subset with 37.38, but the 3rd quartile value changes from 12.00 to 37.38.


## Are there differences in activity patterns between weekdays and weekends?
```{r}

```

